TrueSkill Through Time: the \proglang{Python} Package

### 2020-07-21 article.tex
Paper TTT: implementacion y ejemplo de trueskill vanilla tanto con un loop como de manera simil TTT

\lstinputlisting{./code/Example1.py}

\subsection{Example 2: Trueskill dataset}
For this example  we want to show how trueskill can be used with a data set. For this we will use de as input Table \ref{tab:csvExample2}. Its important to de Result input as shown. In this case we will use the library Pandas, but it can be done with out it, the only important its how to upload the data set and loop with it.

\begin{table}[h!]
	\centering
	%\resizebox{\textwidth}{!}{%
		\begin{tabular}{llll}
			\hline
			Id  & Player1        & Player2        & Result \\ \hline
			101 & 'matt64'       & 'Chuk'         & [1,0]      \\
			102 & 'matt64'       & 'David'        & [1,0]      \\
			103 & 'ggg'          & 'matt64'       & [0,1]      \\
			104 & 'Chuk'         & 'David'        & [0,1]      \\
			105 & 'ggg'          & 'TheProffesor' & [0,1]      \\
			106 & 'ggg'          & 'matt64'       & [1,0]      \\
			107 & 'Chuk'         & 'TheProffesor' & [0,1]      \\
			108 & 'Chuk'         & 'NaT'          & [1,0]      \\
			109 & 'David'        & 'TheProffesor' & [1,0]      \\
			110 & 'David'        & 'Chuk'         & [1,0]      \\
			111 & 'TheProffesor' & 'Chuk'         & [0,1]      \\
			112 & 'Mona'         & 'matt64'       & [1,0]      \\
			113 & 'TiNi'         & 'David'        & [1,0]      \\
			113 & 'Chuk'         & 'matt64'       & [1,0]      \\
			115 & 'ggg'          & 'matt64'       & [1,0]      \\ \hline
		\end{tabular}%
	%}
	\caption{An example of Data set, used in example 2. }
	\label{tab:csvExample2}
\end{table}

\lstinputlisting{./code/Example2.py}
\subsection{Example 3: Trueskill True Time}
One of the advantage of \textbf{TTT}, its the way that the algorithm pass information to de past to the future and vice versa, getting a more accurate estimation. In addition, it can define a temporal batch were its suppose that in there the order of the games it doesn't matter. For that, we use the next example. Three player, three games, that each one wins one game and lose the other one. So if we do trueskill, the order of how we compute the games will have importance, making at the end three player with three different skill. With \textbf{TTT} this kind of problem its solve.

@@

>>>>

\lstinputlisting{./code/Example1.py}
\begin{lstlisting}
[Out]: Posterior:  TrueSkill.Rating(mu=29.205, sigma=7.194, beta=4.167, noise=0.083) Mean:  29.2052208700336 Variance:  7.194481348831081
\end{lstlisting}
\subsection{Example 2: Trueskill dataset}
For this example  we want to show how trueskill can be used with a data set. To start, we will show the implementation for the users that already are familar with the original trueskill package, then we will show the way that this package its intend to be used. With this way, the use of \textbf{TTT} its trivial. For the first and second case we will use de as input Table \ref{tab:csvExample2}. Its important to de Result input as shown. In this first case we will use the library Pandas, but it can be done with out it, the only important its how to upload the data set and loop with it. For the second case we still using Pandas but only to keep the same way of reading the CSV file that the first one. In this case we dont need to loop manually through the data set.

\begin{table}[h!]
	\centering
	%\resizebox{\textwidth}{!}{%
		\begin{tabular}{llll}
			\hline
			Id  & Player1        & Player2        & Result \\ \hline
			101 & matt64      & Chuk         & [1,0]      \\
			102 & matt64      & David        & [1,0]      \\
			103 & ggg          & matt64       & [0,1]      \\
			104 & Chuk         & David        & [0,1]      \\
			105 & ggg         & TheProffesor & [0,1]      \\
			106 & ggg          & matt64       & [1,0]      \\
			107 & Chuk         & TheProffesor & [0,1]      \\
			108 & Chuk         & NaT          & [1,0]      \\
			109 & David        & TheProffesor & [1,0]      \\
			110 & David        & Chuk         & [1,0]      \\
			111 & TheProffesor & Chuk         & [0,1]      \\
			112 & Mona         & matt64       & [1,0]      \\
			113 & TiNi         & David        & [1,0]      \\
			113 & Chuk         & matt64       & [1,0]      \\
			115 & ggg          & matt64       & [1,0]      \\ \hline
		\end{tabular}%
	%}
	\caption{An example of Data set, used in example 2. }
	\label{tab:csvExample2}
\end{table}

\subsubsection{Example 2 old implementation}
As we can see, the implantation requires a more manual job, by defining dictionary and also adding noise to the priors, like the trueskill algorithm suggest. This default noise can be change to other. The only thing we must do manually its to pass the input in the correct format.
\lstinputlisting{./code/Example2.py}

\subsubsection{Example 2 new implementation}
\lstinputlisting{./code/Example2-1.py}

\subsection{Example 3: Trueskill True Time}
One of the advantage of \textbf{TTT}, its the way that the algorithm pass information to de past to the future and vice versa, getting a more accurate estimation. In addition, it can define a temporal batch were its suppose that in there the order of the games it doesn't matter. For that, we use the next example. Three player, three games, that each one wins one game and lose the other one. So if we do trueskill, the order of how we compute the games will have importance, making at the end three player with three different skill. With \textbf{TTT} this kind of problem its solve.

@@

To extend this example to a data set with more games, the only thing that matter is to pass the information in the format show. In first place is the composition of games, that its a list, that contain a list for each game, that it have another list for each team. So its a list of list of list. Then its have a list of list of results, where each element is a list of numbers, representing the result of each team in each game. The next importan input its the time batches, as default it will make each game in a
